Figures

### 2018-07-12 manuscript/figures.Rmd
shrink conceptual fig

```{r fig.cap="Major lake and watershed characteristics, factors, and processes affecting lake P retention. Shaded symbols indicate items typically considered in P retention models while open symbols indicate additional items considered in the present study.", echo=FALSE, fig.width=1}
knitr::include_graphics("../figures/conceptual_p-cycle_pt2.pdf")
```

>>>>

```{r fig.cap="Major lake and watershed characteristics, factors, and processes affecting lake P retention. Shaded symbols indicate items typically considered in P retention models while open symbols indicate additional items considered in the present study.", echo=FALSE, fig.width=1,out.height="4in"}
knitr::include_graphics("../figures/conceptual_p-cycle_pt2.pdf")
```
